---
title: "Fig4: Exiguobacterium R2567-derived cyclo (Leu-Pro) actives rice SL signaling pathway"
author: "HaoranXu"
date: "2024/09/11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Load setting and functions
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
library(reshape2)
```

## Fig4C The D53 protein levels after the treatment of SL analog rac-GR24 and cyclo (Lue-Pro). 

```{r}
#read input files
RawData = read.table("dataForFig4C.csv", header=T, sep=",")
#calculate plot data
phenotype = "RelativeD53Level"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Nip_Mock", "Nip_gr24", "Nip_S6"))
#statistics
ForSig = RawData
ForSig = ForSig[, c("GroupID", phenotype)]
colnames(ForSig)[2] = "y"
TtestResult = compare_means(y ~ GroupID, data = ForSig, method = "t.test", paired = F,)
colnames(ForSig)[2] = phenotype
TtestResult = as.data.frame(TtestResult)
TtestResult = TtestResult[TtestResult$group1 == "Nip_Mock",] 
TtestResult$padjFDR = p.adjust(TtestResult$p, method = "fdr", n = length(TtestResult$p))
TtestResult = TtestResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal = TtestResult
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig4C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
#prepare data for plot
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#666666", "#765005", "#ffc076")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
ggsave(p, filename = "Fig4C.pdf", width = 2, height = 2.5)
#ggsave(p, filename = "Fig4C.png", width = 2, height = 2.5)
```

## Fig4E  Inoculation of cyclo (Leu-Pro) significantly inhibit the tiller numbers of wild-type rice in a time-series manner.

```{r}
#read input files
# 读取实验设计文件赋给因子排序----
RawData = read.table("dataForFig4E.csv", header=T, sep=",")
index = RawData
#calculate plot data
colnames(index)[2:11] <- c(4, 8, 12, 16, 20, 25, 29, 33, 37, 41)
index = melt(index, id.vars = c("GroupID"), variable.name = "GrowthTime", value.name = "TillerNumber")
index$GroupID = factor(index$GroupID, levels = c("Np_Mock", "Np_Gr24", "Np_S6"))
ForPlot = summarySE(index, measurevar = "TillerNumber", groupvars=c("GroupID", "GrowthTime"))
ForPlot$GrowthTime=as.numeric(as.character(ForPlot$GrowthTime))
#statistics
SigTableFinal = t(as.data.frame(c("Days", "group2", "method", "p", "padjFDR"))) 
colnames(SigTableFinal) = c("Days", "group2", "method", "p", "padjFDR")
SigTableFinal = SigTableFinal[-1,]
Days = c("TillerNumber4D", "TillerNumber8D", "TillerNumber12D", "TillerNumber16D", "TillerNumber20D", "TillerNumber25D", "TillerNumber29D", "TillerNumber33D", "TillerNumber37D", "TillerNumber41D")
for (daynumber in Days){
  ForSig = RawData
  ForSig$GroupID = factor(ForSig$GroupID, levels = c("Np_Mock", "Np_Gr24", "Np_S6"))
  ForSig = ForSig[, c("GroupID", daynumber)]
  colnames(ForSig)[2] = "TillerNumber"
  WilcoxtestResult = compare_means(TillerNumber ~ GroupID, data = ForSig, method = "wilcox.test", paired = F)
  colnames(ForSig)[2] = daynumber
  WilcoxtestResult$.y. = daynumber
  WilcoxtestResult = as.data.frame(WilcoxtestResult)
  WilcoxtestResult = WilcoxtestResult[WilcoxtestResult$group1 == "Np_Mock",]
  WilcoxtestResult$padjFDR = p.adjust(WilcoxtestResult$p, method = "fdr", n = length(WilcoxtestResult$p))
  colnames(WilcoxtestResult)[1] = "Days"
  WilcoxtestResult = WilcoxtestResult[, c("Days", "group2", "method", "p", "padjFDR")]
  SigTableFinal = merge(SigTableFinal, WilcoxtestResult, all =T) 
}
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
padjmethod = "padjFDRAsterisk"
SigTableFinal$GroupID = SigTableFinal$group2
SigTableFinal$Days = str_replace(SigTableFinal$Days, "TillerNumber", "")
SigTableFinal$Days = str_replace(SigTableFinal$Days, "D", "")
SigTableFinal$GrowthTime = SigTableFinal$Days
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
SigTableFinal = merge(ForPlot[,c("GroupID", "GrowthTime", "N", "TillerNumber")], SigTableFinal[,c("GroupID", "GrowthTime", "method", "p", "padjFDR","pAsterisk", "padjFDRAsterisk")], by = c("GroupID", "GrowthTime"), all = T)
#write.table(SigTableFinal, file="StatisticsResult.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
SigTableFinal = SigTableFinal[,c("GroupID", "GrowthTime", "padjFDRAsterisk")]
ForPlot = merge(ForPlot, SigTableFinal, all = T)
#save plot
p = ggplot(ForPlot, aes(x = GrowthTime, y = TillerNumber, colour = GroupID, shape = GroupID)) +
  geom_point(shape=16, size=1) +
  geom_line(size=0.5) +
  labs(x=paste("GrowthTime(Days)"), y="TillerNumber") +
  geom_errorbar(aes(ymin = TillerNumber, ymax = TillerNumber+se), width = 0.5) +
  geom_text(data=ForPlot, aes(x=GrowthTime, y= TillerNumber+0.1, label= padjFDRAsterisk),show.legend = FALSE, color="black") +
  xlab("Days after compound inoculation") +
  scale_y_continuous(limits = c(1, 3.2)) +
  scale_color_manual(values = c("#666666", "#765005", "#ffc076")) +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    ) 
ggsave(p, filename = "Fig4E.pdf", width = 5, height = 3)
#ggsave(p, filename = "Fig4E.png", width = 5, height = 3)
```

## Fig4F  Inoculation of cyclo (Leu-Pro) significantly inhibit the tiller numbers of wild-type rice Nipponbare in field condition.

```{r}
#read input files
RawData = read.table("dataForFig4F.csv", header=T, sep=",")

#calculate plot data
phenotype = "TillerNumber"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="Treatment")
ForPlot$Treatment = factor(ForPlot$Treatment, levels = c("Mock", "Gr24", "S6"))

ForSig = RawData
ForSig = ForSig[, c("Treatment", phenotype)]
colnames(ForSig)[2] = "y"
WilcoxonResult = compare_means(y ~ Treatment, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = phenotype
WilcoxonResult = as.data.frame(WilcoxonResult)
WilcoxonResult = WilcoxonResult[WilcoxonResult$group1 == "Mock",]
WilcoxonResult$padjFDR = p.adjust(WilcoxonResult$p, method = "fdr", n = length(WilcoxonResult$p))
WilcoxonResult = WilcoxonResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal = WilcoxonResult
  for (padjmethod in c("p", "padjFDR")){
    asterisk = paste(padjmethod, "Asterisk", sep = "")
    for (m in 1:length(SigTableFinal[,1])){
      ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
              SigTableFinal[[asterisk]][m] <- "***",
              ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                      SigTableFinal[[asterisk]][m] <- "**",
                      ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                              SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
    }
  }
SigTableFinal = merge(ForPlot[,c("Treatment","N", phenotype)], SigTableFinal, by.x = "Treatment", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig5B.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
ForPlot = merge(ForPlot, SigTableFinal[,c("Treatment", "padjFDRAsterisk")], all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = Treatment, y = .data[[phenotype]], fill = Treatment)) +
    geom_bar(stat = "identity", width = 0.8) +
    geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
    geom_text(aes(x = Treatment, y = max, label = padjFDRAsterisk)) +
    ggtitle("Nipponbare") +
    scale_fill_manual(values = c("#888888", "#10885A", "#A3A010")) +
     xlab("") +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
)
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
ggsave(p, filename = "Fig4F.pdf", width = 2, height = 2.5)

```


## Fig4G  Inoculation of cyclo (Leu-Pro) significantly inhibit the tiller numbers of wild-type rice 9311 in field condition.

```{r}
#read input files
RawData = read.table("dataForFig4G.csv", header=T, sep=",")

#calculate plot data
phenotype = "TillerNumber"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="Treatment")
ForPlot$Treatment = factor(ForPlot$Treatment, levels = c("Mock", "Gr24", "S6"))

ForSig = RawData
ForSig = ForSig[, c("Treatment", phenotype)]
colnames(ForSig)[2] = "y"
WilcoxonResult = compare_means(y ~ Treatment, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = phenotype
WilcoxonResult = as.data.frame(WilcoxonResult)
WilcoxonResult = WilcoxonResult[WilcoxonResult$group1 == "Mock",]
WilcoxonResult$padjFDR = p.adjust(WilcoxonResult$p, method = "fdr", n = length(WilcoxonResult$p))
WilcoxonResult = WilcoxonResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal = WilcoxonResult
  for (padjmethod in c("p", "padjFDR")){
    asterisk = paste(padjmethod, "Asterisk", sep = "")
    for (m in 1:length(SigTableFinal[,1])){
      ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
              SigTableFinal[[asterisk]][m] <- "***",
              ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                      SigTableFinal[[asterisk]][m] <- "**",
                      ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                              SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
    }
  }
SigTableFinal = merge(ForPlot[,c("Treatment","N", phenotype)], SigTableFinal, by.x = "Treatment", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig5B.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
ForPlot = merge(ForPlot, SigTableFinal[,c("Treatment", "padjFDRAsterisk")], all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = Treatment, y = .data[[phenotype]], fill = Treatment)) +
    geom_bar(stat = "identity", width = 0.8) +
    geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
    geom_text(aes(x = Treatment, y = max, label = padjFDRAsterisk)) +
    ggtitle("9311") +
    scale_fill_manual(values = c("#888888", "#10885A", "#A3A010")) +
     xlab("") +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
)
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
ggsave(p, filename = "Fig4G.pdf", width = 2, height = 2.5)

```

## Fig4H  Inoculation of cyclo (Leu-Pro) significantly inhibit the tiller numbers of wild-type rice NC1/536 in field condition.

```{r}
#read input files
RawData = read.table("dataForFig4H.csv", header=T, sep=",")

#calculate plot data
phenotype = "TillerNumber"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="Treatment")
ForPlot$Treatment = factor(ForPlot$Treatment, levels = c("Mock", "Gr24", "S6"))

ForSig = RawData
ForSig = ForSig[, c("Treatment", phenotype)]
colnames(ForSig)[2] = "y"
WilcoxonResult = compare_means(y ~ Treatment, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = phenotype
WilcoxonResult = as.data.frame(WilcoxonResult)
WilcoxonResult = WilcoxonResult[WilcoxonResult$group1 == "Mock",]
WilcoxonResult$padjFDR = p.adjust(WilcoxonResult$p, method = "fdr", n = length(WilcoxonResult$p))
WilcoxonResult = WilcoxonResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal = WilcoxonResult
  for (padjmethod in c("p", "padjFDR")){
    asterisk = paste(padjmethod, "Asterisk", sep = "")
    for (m in 1:length(SigTableFinal[,1])){
      ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
              SigTableFinal[[asterisk]][m] <- "***",
              ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                      SigTableFinal[[asterisk]][m] <- "**",
                      ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                              SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
    }
  }
SigTableFinal = merge(ForPlot[,c("Treatment","N", phenotype)], SigTableFinal, by.x = "Treatment", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig5B.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
ForPlot = merge(ForPlot, SigTableFinal[,c("Treatment", "padjFDRAsterisk")], all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = Treatment, y = .data[[phenotype]], fill = Treatment)) +
    geom_bar(stat = "identity", width = 0.8) +
    geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
    geom_text(aes(x = Treatment, y = max, label = padjFDRAsterisk)) +
    ggtitle("NC1/536") +
    scale_fill_manual(values = c("#888888", "#10885A", "#A3A010")) +
     xlab("") +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
)
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
ggsave(p, filename = "Fig4H.pdf", width = 2, height = 2.5)

```

## Fig4I  Inoculation of cyclo (Leu-Pro) significantly inhibit the tiller numbers of wild-type rice Karabaschak in field condition.

```{r}
#read input files
RawData = read.table("dataForFig4I.csv", header=T, sep=",")

#calculate plot data
phenotype = "TillerNumber"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="Treatment")
ForPlot$Treatment = factor(ForPlot$Treatment, levels = c("Mock", "Gr24", "S6"))

ForSig = RawData
ForSig = ForSig[, c("Treatment", phenotype)]
colnames(ForSig)[2] = "y"
WilcoxonResult = compare_means(y ~ Treatment, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = phenotype
WilcoxonResult = as.data.frame(WilcoxonResult)
WilcoxonResult = WilcoxonResult[WilcoxonResult$group1 == "Mock",]
WilcoxonResult$padjFDR = p.adjust(WilcoxonResult$p, method = "fdr", n = length(WilcoxonResult$p))
WilcoxonResult = WilcoxonResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal = WilcoxonResult
  for (padjmethod in c("p", "padjFDR")){
    asterisk = paste(padjmethod, "Asterisk", sep = "")
    for (m in 1:length(SigTableFinal[,1])){
      ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
              SigTableFinal[[asterisk]][m] <- "***",
              ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                      SigTableFinal[[asterisk]][m] <- "**",
                      ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                              SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
    }
  }
SigTableFinal = merge(ForPlot[,c("Treatment","N", phenotype)], SigTableFinal, by.x = "Treatment", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig5B.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
ForPlot = merge(ForPlot, SigTableFinal[,c("Treatment", "padjFDRAsterisk")], all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = Treatment, y = .data[[phenotype]], fill = Treatment)) +
    geom_bar(stat = "identity", width = 0.8) +
    geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
    geom_text(aes(x = Treatment, y = max, label = padjFDRAsterisk)) +
    ggtitle("Karabaschak") +
    scale_fill_manual(values = c("#888888", "#10885A", "#A3A010")) +
     xlab("") +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
)
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
ggsave(p, filename = "Fig4I.pdf", width = 2, height = 2.5)

```

