---
title: "Fig5: Cyclo (Leu-Pro) directly binds rice strigolactone receptor D14"
author: "HaoranXu"
date: "2024/09/12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Load setting and functions
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
library(reshape2)
library(stringr)
library(tidyr)
library(plyr)
```

## Fig5A Quantification of binding between SL analog rac-GR24 and D14 by microscale thermophoresis (MST).

```{r}
#read input files
RawData = read.table("dataForFig5AB.csv", header=T, sep=",")
index = RawData
D14GR24 = index[index$GroupID == "OsD14_GR24",]

# normalization
D14GR24 = D14GR24 %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "Concentration",
               values_to = "FractionBound")

D14GR24$Concentration <- as.numeric(sub("^X", "", D14GR24$Concentration))
D14GR24 = summarySE(D14GR24, measurevar = "FractionBound", groupvars=c("Concentration"))
D14GR24 = D14GR24[,c("Concentration", "FractionBound", "sd")]
D14GR24$norm = (D14GR24$FractionBound - min(D14GR24$FractionBound)) / (max(D14GR24$FractionBound) - min(D14GR24$FractionBound))
D14GR24$log10Concentration = log10(D14GR24$Concentration)
D14GR24 = rbind(c(0,0,0,0),D14GR24)  

# lm
model <- glm(norm ~ log10Concentration, data = D14GR24, family = binomial(link = "logit"))
x_new <- seq(min(D14GR24$log10Concentration), max(D14GR24$log10Concentration)+0.2, length.out = 100)
y_pred <- predict(model, data.frame(log10Concentration = x_new), type = "response")
Linedata <- data.frame(x = x_new, y = y_pred * (max(D14GR24$FractionBound) - min(D14GR24$FractionBound)) + min(D14GR24$FractionBound))
D14GR24 = D14GR24[-1,]
  
  
p = ggplot(D14GR24, aes(x = log10Concentration, y = FractionBound)) +
geom_point(shape=16, size=1) +
geom_errorbar(aes(ymin = FractionBound-sd, ymax = FractionBound+sd), width = 0.1) +
geom_line(data = Linedata, aes(x = x, y = y), color = "black") +
xlim(1.6, 5.5) +
ylim(-0.2, 1.2) +
labs(title = "D14-GR24", x = paste("Concentration(uM)"), y = "FractionBound", color = "black", size = 8) +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#ggsave(p, filename = "Fig5A.png", width = 2.3, height = 2)
ggsave(p, filename = "Fig5A.pdf", width = 2.3, height = 2)

```

## Fig5B Quantification of binding between SL analog cyclo (Leu-Pro) and D14 by microscale thermophoresis (MST).

```{r}
#read input files
RawData = read.table("dataForFig5AB.csv", header=T, sep=",")
index = RawData
D14S6 = index[index$GroupID == "OsD14_S6",]

# normalization
D14S6 = D14S6 %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "Concentration",
               values_to = "FractionBound")

D14S6$Concentration <- as.numeric(sub("^X", "", D14S6$Concentration))
D14S6 = summarySE(D14S6, measurevar = "FractionBound", groupvars=c("Concentration"))
D14S6 = D14S6[,c("Concentration", "FractionBound", "sd")]
D14S6$norm = (D14S6$FractionBound - min(D14S6$FractionBound)) / (max(D14S6$FractionBound) - min(D14S6$FractionBound))
D14S6$log10Concentration = log10(D14S6$Concentration)
D14S6 = rbind(c(0,0,0,0),D14S6)  

# lm
model <- glm(norm ~ log10Concentration, data = D14S6, family = binomial(link = "logit"))
x_new <- seq(min(D14S6$log10Concentration), max(D14S6$log10Concentration)+0.2, length.out = 100)
y_pred <- predict(model, data.frame(log10Concentration = x_new), type = "response")
Linedata <- data.frame(x = x_new, y = y_pred * (max(D14S6$FractionBound) - min(D14S6$FractionBound)) + min(D14S6$FractionBound))
D14S6 = D14S6[-1,]
  
  
p = ggplot(D14S6, aes(x = log10Concentration, y = FractionBound)) +
geom_point(shape=16, size=1) +
geom_errorbar(aes(ymin = FractionBound-sd, ymax = FractionBound+sd), width = 0.1) +
geom_line(data = Linedata, aes(x = x, y = y), color = "black") +
xlim(1.6, 5.5) +
ylim(-0.2, 1.2) +
labs(title = "D14-S6", x = paste("Concentration(uM)"), y = "FractionBound", color = "black", size = 8) +
  theme(
  plot.background = element_rect(fill = "#FFFFFF"), 
  panel.background = element_blank(), 
  panel.grid.major.x = element_blank(),
  panel.grid.major.y = element_blank(), 
  panel.grid.minor.x = element_blank(), 
  panel.grid.minor.y = element_blank(),
  panel.border = element_blank(), 
  axis.title = element_text(size = 8),  
  axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
  axis.line = element_line(colour = "#000000"),
  legend.title = element_blank(),
  legend.key = element_rect(fill = "#FFFFFF"),
  legend.position = "none"
  )
#ggsave(p, filename = "Fig5B.png", width = 2.3, height = 2)
ggsave(p, filename = "Fig5B.pdf", width = 2.3, height = 2)

```

## Fig5E-F Quantification of binding between SL analog rac-GR24 and D14 mutants by microscale thermophoresis (MST).

```{r}
#read input files
RawData = read.table("dataForFig5E_F.csv", header=T, sep=",")
index = RawData
OsD14F186A = index[index$GroupID == "OsD14F186A_S6",]
OsD14V269D = index[index$GroupID == "OsD14V269D_S6",]
OsD14F245A = index[index$GroupID == "OsD14F245A_S6",]
OsD14L212D = index[index$GroupID == "OsD14L212D_S6",]

# F186A
# normalization
OsD14F186A = OsD14F186A %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "Concentration",
               values_to = "FractionBound")

OsD14F186A$Concentration <- as.numeric(sub("^X", "", OsD14F186A$Concentration))
OsD14F186A = summarySE(OsD14F186A, measurevar = "FractionBound", groupvars=c("Concentration"))
OsD14F186A = OsD14F186A[,c("Concentration", "FractionBound", "sd")]
OsD14F186A$norm = (OsD14F186A$FractionBound - min(OsD14F186A$FractionBound)) / (max(OsD14F186A$FractionBound) - min(OsD14F186A$FractionBound))
OsD14F186A$log10Concentration = log10(OsD14F186A$Concentration)
OsD14F186A = rbind(c(0,0,0,0),OsD14F186A)  

# lm
model <- glm(norm ~ log10Concentration, data = OsD14F186A, family = binomial(link = "logit"))
x_new <- seq(min(OsD14F186A$log10Concentration), max(OsD14F186A$log10Concentration)+0.2, length.out = 100)
y_pred <- predict(model, data.frame(log10Concentration = x_new), type = "response")
Linedata <- data.frame(x = x_new, y = y_pred * (max(OsD14F186A$FractionBound) - min(OsD14F186A$FractionBound)) + min(OsD14F186A$FractionBound))
OsD14F186A = OsD14F186A[-1,]
  
p = ggplot(OsD14F186A, aes(x = log10Concentration, y = FractionBound)) +
geom_point(shape=16, size=1) +
geom_errorbar(aes(ymin = FractionBound-sd, ymax = FractionBound+sd), width = 0.1) +
geom_line(data = Linedata, aes(x = x, y = y), color = "black") +
xlim(1.6, 5.5) +
ylim(-0.2, 1.2) +
labs(title = "OsD14F186A", x = paste("Concentration(uM)"), y = "FractionBound", color = "black", size = 8) +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#ggsave(p, filename = "Fig5E_1.png", width = 2.3, height = 2)
ggsave(p, filename = "Fig5E_1.pdf", width = 2.3, height = 2)


# V269D
# normalization
OsD14V269D = OsD14V269D %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "Concentration",
               values_to = "FractionBound")

OsD14V269D$Concentration <- as.numeric(sub("^X", "", OsD14V269D$Concentration))
OsD14V269D = summarySE(OsD14V269D, measurevar = "FractionBound", groupvars=c("Concentration"))
OsD14V269D = OsD14V269D[,c("Concentration", "FractionBound", "sd")]
OsD14V269D$log10Concentration = log10(OsD14V269D$Concentration)

p = ggplot(OsD14V269D, aes(x = log10Concentration, y = FractionBound)) +
geom_point(shape=16, size=1) +
geom_errorbar(aes(ymin = FractionBound-sd, ymax = FractionBound+sd), width = 0.1) +
#geom_line(data = Linedata, aes(x = x, y = y), color = "black") +
xlim(1.6, 5.5) +
#ylim(-0.2, 1.2) +
labs(title = "D14V269D", x = paste("Concentration(uM)"), y = "FractionBound", color = "black", size = 8) +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#ggsave(p, filename = "Fig5F_2.png", width = 2.3, height = 2)
ggsave(p, filename = "Fig5F_2.pdf", width = 2.3, height = 2)


# F245A
OsD14F245A = OsD14F245A %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "Concentration",
               values_to = "FractionBound")

OsD14F245A$Concentration <- as.numeric(sub("^X", "", OsD14F245A$Concentration))
OsD14F245A = summarySE(OsD14F245A, measurevar = "FractionBound", groupvars=c("Concentration"))
OsD14F245A = OsD14F245A[,c("Concentration", "FractionBound", "sd")]
OsD14F245A$norm = (OsD14F245A$FractionBound - min(OsD14F245A$FractionBound)) / (max(OsD14F245A$FractionBound) - min(OsD14F245A$FractionBound))
OsD14F245A$log10Concentration = log10(OsD14F245A$Concentration)
OsD14F245A = rbind(c(0,0,0,0),OsD14F245A)  

# lm
model <- glm(norm ~ log10Concentration, data = OsD14F245A, family = binomial(link = "logit"))
x_new <- seq(min(OsD14F245A$log10Concentration), max(OsD14F245A$log10Concentration)+0.2, length.out = 100)
y_pred <- predict(model, data.frame(log10Concentration = x_new), type = "response")
Linedata <- data.frame(x = x_new, y = y_pred * (max(OsD14F245A$FractionBound) - min(OsD14F245A$FractionBound)) + min(OsD14F245A$FractionBound))
OsD14F245A = OsD14F245A[-1,]
  
p = ggplot(OsD14F245A, aes(x = log10Concentration, y = FractionBound)) +
geom_point(shape=16, size=1) +
geom_errorbar(aes(ymin = FractionBound-sd, ymax = FractionBound+sd), width = 0.1) +
geom_line(data = Linedata, aes(x = x, y = y), color = "black") +
xlim(1.6, 5.5) +
ylim(-0.2, 1.2) +
labs(title = "D14F245A", x = paste("Concentration(uM)"), y = "FractionBound", color = "black", size = 8) +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#ggsave(p, filename = "Fig5E_2.png", width = 2.3, height = 2)
ggsave(p, filename = "Fig5E_2.pdf", width = 2.3, height = 2)


# L212D
OsD14L212D = OsD14L212D %>%
  pivot_longer(cols = starts_with("X"),
               names_to = "Concentration",
               values_to = "FractionBound")

OsD14L212D$Concentration <- as.numeric(sub("^X", "", OsD14L212D$Concentration))
OsD14L212D = summarySE(OsD14L212D, measurevar = "FractionBound", groupvars=c("Concentration"))
OsD14L212D = OsD14L212D[,c("Concentration", "FractionBound", "sd")]
OsD14L212D$norm = (OsD14L212D$FractionBound - min(OsD14L212D$FractionBound)) / (max(OsD14L212D$FractionBound) - min(OsD14L212D$FractionBound))
OsD14L212D$log10Concentration = log10(OsD14L212D$Concentration)
OsD14L212D = rbind(c(0,0,0,0),OsD14L212D)  

# lm
model <- glm(norm ~ log10Concentration, data = OsD14L212D, family = binomial(link = "logit"))
x_new <- seq(min(OsD14L212D$log10Concentration), max(OsD14L212D$log10Concentration)+0.2, length.out = 100)
y_pred <- predict(model, data.frame(log10Concentration = x_new), type = "response")
Linedata <- data.frame(x = x_new, y = y_pred * (max(OsD14L212D$FractionBound) - min(OsD14L212D$FractionBound)) + min(OsD14L212D$FractionBound))
OsD14L212D = OsD14L212D[-1,]
  
p = ggplot(OsD14L212D, aes(x = log10Concentration, y = FractionBound)) +
geom_point(shape=16, size=1) +
geom_errorbar(aes(ymin = FractionBound-sd, ymax = FractionBound+sd), width = 0.1) +
geom_line(data = Linedata, aes(x = x, y = y), color = "black") +
xlim(1.6, 5.5) +
ylim(-0.2, 1.2) +
labs(title = "D14L212D", x = paste("Concentration(uM)"), y = "FractionBound", color = "black", size = 8) +
    theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#ggsave(p, filename = "Fig5F_1.png", width = 2.3, height = 2)
ggsave(p, filename = "Fig5F_1.pdf", width = 2.3, height = 2)

```

## Fig5G Mutations in D14 eliminate the effect of cyclo (Leu-Pro) on D53 degradation. 

```{r}
#read input files
RawData = read.table("dataForFig5G.csv", header=T, sep=",")
#calculate plot data
phenotype = "RelativeD53Level"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Nip_Mock", "Nip_gr24", "Nip_S6", "d14_Mock", "d14_gr24", "d14_S6"))
#statistics
ForSig = RawData
colnames(ForSig)[2] = "y"
TtestResult = compare_means(y ~ GroupID, data = ForSig, method = "t.test", paired = F,)
colnames(ForSig)[2] = phenotype
TtestResult = as.data.frame(TtestResult)
TtestResult = TtestResult[c(1,2,3,13,14),]
TtestResult$padjFDR = p.adjust(TtestResult$p, method = "fdr", n = length(TtestResult$p))
TtestResult = TtestResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal = TtestResult
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig4C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
#prepare data for plot
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#765005", "#ffc076", "#888888", "#765005", "#ffc076")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
ggsave(p, filename = "Fig5G.pdf", width = 3.5, height = 2.5)
#ggsave(p, filename = "Fig5G.png", width = 3.5, height = 2.5)

```

## Fig5H  Mutations in D14 eliminate the tiller-inhibiting effect of cyclo (Leu-Pro) under the hydroponic condition

```{r}
# read input files
RawData = read.table("dataForFig5H.csv", header=T, sep=",")
index = RawData
index = index[index$GroupID %in% c("Np_Mock", "Np_Gr24", "Np_S6"),]
ForPlot <- summarySE(index, measurevar = "TillerNumber", groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Np_Mock", "Np_Gr24", "Np_S6", "d14_Mock", "d14_Gr24", "d14_S6"))

#statistics
ForSig = index
colnames(ForSig)[2] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = "TillerNumber"
WilcoxtestResult = as.data.frame(WilcoxtestResult)
SigTableFinal = WilcoxtestResult[c(1,2),]
SigTableFinal$padjFDR = p.adjust(SigTableFinal$p, method = "fdr", n = length(SigTableFinal$p))
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", "TillerNumber")], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig4C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
#prepare data for plot
ForPlot$max = (ForPlot$TillerNumber + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = TillerNumber, fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = TillerNumber, ymax = TillerNumber+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#10885A", "#A3A010","#888888", "#10885A", "#A3A010")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
#ggsave(p, filename = "Fig5H_1.png", width = 2, height = 3)
ggsave(p, filename = "Fig5H_1.pdf", width = 2, height = 3)


index = RawData
index = index[index$GroupID %in% c("d14_Mock", "d14_Gr24", "d14_S6"),]
ForPlot <- summarySE(index, measurevar = "TillerNumber", groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Np_Mock", "Np_Gr24", "Np_S6", "d14_Mock", "d14_Gr24", "d14_S6"))

#statistics
ForSig = index
colnames(ForSig)[2] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = "TillerNumber"
WilcoxtestResult = as.data.frame(WilcoxtestResult)
SigTableFinal = WilcoxtestResult[c(1,2),]
SigTableFinal$padjFDR = p.adjust(SigTableFinal$p, method = "fdr", n = length(SigTableFinal$p))
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", "TillerNumber")], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig4C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
#prepare data for plot
ForPlot$max = (ForPlot$TillerNumber + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = TillerNumber, fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = TillerNumber, ymax = TillerNumber+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#10885A", "#A3A010","#888888", "#10885A", "#A3A010")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
#ggsave(p, filename = "Fig5H_2.png", width = 2, height = 3)
ggsave(p, filename = "Fig5H_2.pdf", width = 2, height = 3)

```

## Fig5I  Mutations in D14 eliminate the tiller-inhibiting effect of cyclo (Leu-Pro) under the field condition

```{r}
# read input files
RawData = read.table("dataForFig5I.csv", header=T, sep=",")
index = RawData
index = index[index$GroupID %in% c("Np_Mock", "Np_Gr24", "Np_S6"),]
ForPlot <- summarySE(index, measurevar = "TillerNumber", groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Np_Mock", "Np_Gr24", "Np_S6", "d14_Mock", "d14_Gr24", "d14_S6"))

#statistics
ForSig = index
colnames(ForSig)[2] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = "TillerNumber"
WilcoxtestResult = as.data.frame(WilcoxtestResult)
SigTableFinal = WilcoxtestResult[c(1,2),]
SigTableFinal$padjFDR = p.adjust(SigTableFinal$p, method = "fdr", n = length(SigTableFinal$p))
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", "TillerNumber")], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig4C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
#prepare data for plot
ForPlot$max = (ForPlot$TillerNumber + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = TillerNumber, fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = TillerNumber, ymax = TillerNumber+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#10885A", "#A3A010","#888888", "#10885A", "#A3A010")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
p
#ggsave(p, filename = "Fig5I_1.png", width = 2, height = 3)
ggsave(p, filename = "Fig5I_1.pdf", width = 2, height = 3)


index = RawData
index = index[index$GroupID %in% c("d14_Mock", "d14_Gr24", "d14_S6"),]
ForPlot <- summarySE(index, measurevar = "TillerNumber", groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Np_Mock", "Np_Gr24", "Np_S6", "d14_Mock", "d14_Gr24", "d14_S6"))

#statistics
ForSig = index
colnames(ForSig)[2] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = "TillerNumber"
WilcoxtestResult = as.data.frame(WilcoxtestResult)
SigTableFinal = WilcoxtestResult[c(1,2),]
SigTableFinal$padjFDR = p.adjust(SigTableFinal$p, method = "fdr", n = length(SigTableFinal$p))
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", "TillerNumber")], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig4C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
#prepare data for plot
ForPlot$max = (ForPlot$TillerNumber + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = TillerNumber, fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = TillerNumber, ymax = TillerNumber+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#10885A", "#A3A010","#888888", "#10885A", "#A3A010")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
#ggsave(p, filename = "Fig5I_2.png", width = 2, height = 3)
ggsave(p, filename = "Fig5I_2.pdf", width = 2, height = 3)

```
