---
title: "Fig2: Cultivated root microbiota members play causal roles in regulating rice tiller number"
author: "HaoranXu"
date: "2024/09/10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Load setting and functions
library(ggplot2)
library(ggridges)
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
```

## Fig2A Cultivated bacterial isolates in tillered-related genera regulate rice tiller numbers under the laboratory conditions. Z-scored distributions of rice tillers after inoculation of individual isolates in tiller-related genera shown in Ridgeline plots.

```{r}
#read input files
RawData = read.table("dataForFig2AB.csv", header=T, sep=",")
#Plot
ForPlot = RawData
ForPlot$Z_Score = scale(ForPlot$TillerNumber)
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("R2188","R780","R1625","R2149","R1801","R3062","R2797","R1405","R2488","R1870","R1275","R2567","Mock"))
Colormap <- brewer.pal(11,"RdYlBu") 
Colormap <- rev(Colormap)
#save plot
p = ggplot(ForPlot, aes(x = Z_Score, y = GroupID, fill = stat(x))) + 
    geom_density_ridges_gradient(scale = 3, rel_min_height = 0.01) +
    scale_fill_gradientn(colours = Colormap) +
    theme_ridges(grid = FALSE) +
    ylab("") +
    theme(
      plot.background = element_rect(fill = "#FFFFFF"), 
      panel.background = element_blank(), 
      panel.grid.major.x = element_blank(),
      panel.grid.major.y = element_blank(), 
      panel.grid.minor.x = element_blank(), 
      panel.grid.minor.y = element_blank(),
      panel.border = element_blank(), 
      axis.title = element_text(size = 8),  
      axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
      axis.line = element_line(colour = "#000000"),
      legend.title = element_blank(),
      legend.key = element_rect(fill = "#FFFFFF"),
      legend.position = "none"
    )
ggsave(p,filename=paste("Fig2A.pdf"), width=5.5, height=3.8)
#ggsave(p,filename=paste("Fig2A.png"), width=5.5, height=3.8)
```

## Fig2B The number of rice tillers after inoculation of individual isolates in tiller-related genera shown in bar plots.

```{r}
#read input files
RawData = read.table("dataForFig2AB.csv", header=T, sep=",")
phenotype = "TillerNumber"


#calculate plot data
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("R2188","R780","R1625","R2149","R1801","R3062","R2797","R1405","R2488","R1870","R1275","R2567","Mock"))
#statistics
#Wilcox.test
ForSig = RawData
ForSig = ForSig[, c("GroupID", phenotype)]
colnames(ForSig)[2] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[2] = phenotype
WilcoxtestResult = as.data.frame(WilcoxtestResult)
WilcoxtestResult = WilcoxtestResult[WilcoxtestResult$group1 == "Mock",]
WilcoxtestResult$padjFDR = p.adjust(WilcoxtestResult$p, method = "fdr", n = length(WilcoxtestResult$p))
SigTableFinal = WilcoxtestResult[, c("group2", "method", "p", "padjFDR")]
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
padjmethod = "padjFDRAsterisk"
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig2B.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$max = (ForPlot$TillerNumber + ForPlot$se)*1.2
#save data
p = ggplot(data = ForPlot, mapping = aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) + 
  labs(x = "", y="TillerNmuber")  +
  scale_fill_manual(values = c("#fb8d81","#fb8d81","#fb8d81","#fb8d81","#fb8d81","#00c8ce","#00c8ce","#00c8ce","#00c8ce","#00c8ce","#00c8ce","#00c8ce","#888888")) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]] + se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  coord_flip() + 
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
ggsave(p,filename = "Fig2B.pdf", width = 3, height = 3.5)
#ggsave(p,filename = "Fig2B.png", width = 3, height = 3.5)

```
 
## Fig2C-E The isolates in five tiller-related bacterial genera regulate rice tiller number (C) spike number (D) and dry weight (E) under the field conditions.

```{r}
#read input files
RawData = read.table("dataForFig2CDE.csv", header=T, sep=",")
phenotypeList = c("TillerNumber","SpikeNumber","DryWeight")
for (phenotype in phenotypeList) {
  #calculate plot data
  ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
  ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Mock", "R2567", "R2488", "R1405", "R780", "R1801"))
  #statistics
  #Wilcox.test
  ForSig = RawData
  ForSig = ForSig[, c("GroupID", phenotype)]
  ForSig$GroupID = factor(ForSig$GroupID, levels = c("Mock", "R2567", "R2488", "R1405", "R780", "R1801"))
  colnames(ForSig)[2] = "y"
  WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
  colnames(ForSig)[2] = phenotype
  WilcoxtestResult = as.data.frame(WilcoxtestResult)
  WilcoxtestResult = WilcoxtestResult[WilcoxtestResult$group1 == "Mock",]
  WilcoxtestResult$padjFDR = p.adjust(WilcoxtestResult$p, method = "fdr", n = length(WilcoxtestResult$p))
  SigTableFinal = WilcoxtestResult[, c("group2", "method", "p", "padjFDR")]
  for (padjmethod in c("p", "padjFDR")){
    asterisk = paste(padjmethod, "Asterisk", sep = "")
    for (m in 1:length(SigTableFinal[,1])){
      ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
              SigTableFinal[[asterisk]][m] <- "***",
              ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                      SigTableFinal[[asterisk]][m] <- "**",
                      ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                              SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
    }
  }
padjmethod = "padjFDRAsterisk"
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file=paste0("StatisticsResultForFig2CDE", phenotype, ".csv"),append = F, quote = F, sep = ",", row.names = F, col.names = T)
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
ForPlot$padjmethod = padjmethod

#prepare data for plot
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$padjmethod = padjmethod
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) +
  #geom_bar(stat = "identity", width = 0.8) +
  #geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
  geom_boxplot(data = ForSig, aes(x = GroupID, y = .data[[phenotype]], color = GroupID), alpha=0.75, outlier.alpha=0, size=0.7, width=0.5) +
  geom_jitter(data = ForSig, aes(x = GroupID, y = .data[[phenotype]], color = GroupID), size=0.5, alpha=0.7, width = 0.2, height = 0.02)+theme(legend.position="none") +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#00c8ce", "#00c8ce", "#00c8ce", "#fb8d81", "#fb8d81", "#fb8d81", "#fb8d81")) +
  scale_color_manual(values = c("#888888", "#00c8ce", "#00c8ce", "#00c8ce", "#fb8d81", "#fb8d81", "#fb8d81", "#fb8d81")) +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )

p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
#ggsave(p, filename = paste0("Fig2CDE_", phenotype, ".png"), width = 2.4, height = 2.2)
ggsave(p, filename = paste0("Fig2CDE_", phenotype, ".pdf"), width = 2.4, height = 2.2)
}


```