---
title: "Fig3: Exiguobacterium R2567 and Roseateles R780 regulate rice tillering through the strigolactone pathway"
author: "HaoranXu"
date: "2024/09/11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Clean workspace
rm(list=ls()) 
# Load setting and functions
library(ggplot2)
library(RColorBrewer)
library(ggpubr)
library(Rmisc)
```

## Fig3B Exiguobacterium R2567 and Roseateles R780 affect D53 protein levels in rice.

```{r}
#read input files
RawData = read.table("dataForFig3B.csv", header=T, sep=",")
#calculate plot data
phenotype = "RelativeD53Level"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Mock", "R2567", "R2488", "R1405", "R780", "R1801"))
#statistics
ForSig = RawData
ForSig = ForSig[, c("GroupID", phenotype)]
colnames(ForSig)[2] = "y"
TtestResult = compare_means(y ~ GroupID, data = ForSig, method = "t.test", paired = F,)
colnames(ForSig)[2] = phenotype
TtestResult = as.data.frame(TtestResult)
TtestResult = TtestResult[TtestResult$group1 == "Mock",]
TtestResult$padjFDR = p.adjust(TtestResult$p, method = "fdr", n = length(TtestResult$p))
SigTableFinal = TtestResult[, c("group2", "method", "p", "padjFDR")]
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig3B.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)

padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
ForPlot = merge(ForPlot, SigTableFinal[,c("GroupID", "asterisk")], all = T)
ForPlot$padjmethod = padjmethod
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.2
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888", "#00c8ce", "#00c8ce", "#00c8ce",  "#fb8d81", "#fb8d81", "#fb8d81")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave(p, filename = "Fig3B.pdf", width = 3.5, height = 2.5)
#ggsave(p, filename = "Fig3B.png", width = 3.5, height = 2.5)
```

## Fig3C Contents of predominant rice strigolactone 4-deoxyorobanchol (4DO) in root exudates of wild-type rice seedlings after inoculation with Roseateles R780.

```{r}
#read input files
RawData = read.table("dataForFig3C.csv", header=T, sep=",")
#calculate plot data
phenotype = "X4DOInRootExudates"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Mock", "R780"))
#statistics
#T.test
ForSig = RawData
ForSig = ForSig[, c("GroupID", phenotype)]
colnames(ForSig)[2] = "y"
TtestResult = compare_means(y ~ GroupID, data = ForSig, method = "t.test", paired = F,)
colnames(ForSig)[2] = phenotype
TtestResult = as.data.frame(TtestResult)
TtestResult$padjFDR = p.adjust(TtestResult$p, method = "fdr", n = length(TtestResult$p))
TtestResult = TtestResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal =  TtestResult
#asterisk
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig3C.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
SigTableFinal = SigTableFinal[,c("GroupID", "asterisk")]
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.05
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888","#F78FB3")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#  "#4DA2E2", 
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave(p, filename = "Fig3C.pdf", width = 1.25, height = 2.5)
#ggsave(p, filename = "Fig3C.png", width = 1.25, height = 2.5)
```

## Fig3D Contents of predominant rice strigolactone 4-deoxyorobanchol (4DO) in root exudates of wild-type rice seedlings after inoculation with Exiguobacterium R2567.

```{r}
#read input files
RawData = read.table("dataForFig3D.csv", header=T, sep=",")
#calculate plot data
phenotype = "X4DOInRootExudates"
ForPlot <- summarySE(RawData, measurevar = phenotype, groupvars ="GroupID")
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Mock", "R2567"))
#statistics
#T.test
ForSig = RawData
ForSig = ForSig[, c("GroupID", phenotype)]
colnames(ForSig)[2] = "y"
TtestResult = compare_means(y ~ GroupID, data = ForSig, method = "t.test", paired = F,)
colnames(ForSig)[2] = phenotype
TtestResult = as.data.frame(TtestResult)
TtestResult$padjFDR = p.adjust(TtestResult$p, method = "fdr", n = length(TtestResult$p))
TtestResult = TtestResult[, c("group2", "method", "p", "padjFDR")]
SigTableFinal =  TtestResult
#asterisk
for (padjmethod in c("p", "padjFDR")){
  asterisk = paste(padjmethod, "Asterisk", sep = "")
  for (m in 1:length(SigTableFinal[,1])){
    ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
            SigTableFinal[[asterisk]][m] <- "***",
            ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                    SigTableFinal[[asterisk]][m] <- "**",
                    ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                            SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
  }
}
SigTableFinal = merge(ForPlot[,c("GroupID","N", phenotype)], SigTableFinal, by.x = "GroupID", by.y = "group2", all = T)
#write.table(SigTableFinal, file="StatisticsResultForFig3D.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
padjmethod = "padjFDRAsterisk"
SigTableFinal$asterisk = SigTableFinal[[padjmethod]]
SigTableFinal = SigTableFinal[,c("GroupID", "asterisk")]
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$padjmethod = padjmethod
#prepare data for plot
ForPlot = merge(ForPlot, SigTableFinal, all = T)
ForPlot$max = (ForPlot[[phenotype]] + ForPlot$se)*1.05
#save plot
p = ggplot(data = ForPlot, aes(x = GroupID, y = .data[[phenotype]], fill = GroupID)) +
  geom_bar(stat = "identity", width = 0.8) +
  geom_errorbar(aes(ymin = .data[[phenotype]], ymax = .data[[phenotype]]+se), width = .1) +
  geom_text(aes(x = GroupID, y = max, label = asterisk)) +
  scale_fill_manual(values = c("#888888","#4DA2E2")) +
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
    )
#  "#4DA2E2", 
p = p + theme(axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1))
ggsave(p, filename = "Fig3D.pdf", width = 1.25, height = 2.5)
#ggsave(p, filename = "Fig3D.png", width = 1.25, height = 2.5)
```


## Fig3E The effects of Roseateles R780 on tillering of wild-type and mutants rice in SL biosynthesis and signaling.

```{r}

#read input files
RawData = read.table("dataForFig3E.csv", header=T, sep=",")
phenotype = "TillerNumber"
ForPlot = RawData
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Nip_Mock", "Nip_R780", "d14_Mock", "d14_R780", "d27_Mock", "d27_R780"))

# statistics
ForSig = ForPlot
colnames(ForSig)[4] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[4] = phenotype
WilcoxtestResult = as.data.frame(WilcoxtestResult)
WilcoxtestResult = WilcoxtestResult[c(1,10,15),]
WilcoxtestResult = WilcoxtestResult[, c("group2", "method", "p")]
WilcoxtestResult$padjFDR = p.adjust(WilcoxtestResult$p, method = "fdr", n = length(WilcoxtestResult$p))
asterisk = paste(padjmethod, "Asterisk", sep = "")
SigTableFinal = WilcoxtestResult
#write.table(SigTableFinal, file="StatisticsResultForFig3E.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
padjmethod = "padjFDR"
for (m in 1:length(SigTableFinal[,1])){
  ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
          SigTableFinal[[asterisk]][m] <- "***",
          ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                  SigTableFinal[[asterisk]][m] <- "**",
                  ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                          SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
}



# Plot
ForPlot = ForPlot[, c("GroupID", phenotype)]
#calculate plot data
ForPlot <- summarySE(ForPlot, measurevar = phenotype, groupvars ="GroupID")
ForPlot$max=(ForPlot[[phenotype]]+ForPlot$se)+0.3
colnames(SigTableFinal)[1] = "GroupID"
ForPlot = merge(ForPlot, SigTableFinal[c("GroupID", "padjFDRAsterisk")], by = "GroupID", all = T)

#save plot Nip
p1 = ggplot(data = ForPlot[c(1,2),], mapping = aes(x = GroupID, y = .data[[phenotype]], color = GroupID)) + 
  geom_errorbar(aes(ymin = .data[[phenotype]] - se, ymax = .data[[phenotype]] + se), width = .1, color = "black") +
  geom_point(shape = 16, size = 1.5) +
  geom_text(mapping = aes(x = GroupID, y = .data[[phenotype]] + se, label= padjFDRAsterisk)) +
  scale_y_continuous(limits = c(4, 7)) +
  scale_shape_discrete(solid = F) +
  scale_color_manual(values = c("#888888", "#fb8d81")) +
  #00c8ce #fb8d81
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
  )
p1=p1+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
ggsave(p1, filename = "Fig3E_1.pdf", width = 1, height = 2)
#ggsave(p1, filename = "Fig3E_1.png", width = 1, height = 2)

#save plot d14
p2 = ggplot(data = ForPlot[c(3,4),], mapping = aes(x = GroupID, y = .data[[phenotype]], color = GroupID)) + 
  geom_errorbar(aes(ymin = .data[[phenotype]] - se, ymax = .data[[phenotype]] + se), width = .1, color = "black") +
  geom_point(shape = 16, size = 1.5) +
  geom_text(mapping = aes(x = GroupID, y = .data[[phenotype]] + se, label= padjFDRAsterisk)) +
  scale_y_continuous(limits = c(8, 11)) +
  scale_shape_discrete(solid = F) +
  scale_color_manual(values = c("#888888", "#fb8d81")) +
  #00c8ce #fb8d81
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
  )
p2=p2+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
ggsave(p2, filename = "Fig3E_2.pdf", width = 1, height = 2)
#ggsave(p2, filename = "Fig3E_2.png", width = 1, height = 2)
    
#save plot d27
p3 = ggplot(data = ForPlot[c(5,6),], mapping = aes(x = GroupID, y = .data[[phenotype]], color = GroupID)) + 
  geom_errorbar(aes(ymin = .data[[phenotype]] - se, ymax = .data[[phenotype]] + se), width = .1, color = "black") +
  geom_point(shape = 16, size = 1.5) +
  geom_text(mapping = aes(x = GroupID, y = .data[[phenotype]] + se, label= padjFDRAsterisk)) +
  scale_y_continuous(limits = c(5, 8)) +
  scale_shape_discrete(solid = F) +
  scale_color_manual(values = c("#888888", "#fb8d81")) +
  #00c8ce #fb8d81
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
  )
p3=p3+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
ggsave(p3, filename = "Fig3E_3.pdf", width = 1, height = 2)
#ggsave(p3, filename = "Fig3E_3.png", width = 1, height = 2)
```

## Fig3F The effects of Exiguobacterium R2567 on tillering of wild-type and mutants rice in SL biosynthesis and signaling.

```{r}

#read input files
RawData = read.table("dataForFig3F.csv", header=T, sep=",")
phenotype = "TillerNumber"
ForPlot = RawData
ForPlot$GroupID = factor(ForPlot$GroupID, levels = c("Nip_Mock", "Nip_R2567", "d14_Mock", "d14_R2567", "d27_Mock", "d27_R2567"))

# statistics
ForSig = ForPlot
colnames(ForSig)[4] = "y"
WilcoxtestResult = compare_means(y ~ GroupID, data = ForSig, method = "wilcox.test", paired = F,)
colnames(ForSig)[4] = phenotype
WilcoxtestResult = as.data.frame(WilcoxtestResult)
WilcoxtestResult = WilcoxtestResult[c(1,10,15),]
WilcoxtestResult = WilcoxtestResult[, c("group2", "method", "p")]
WilcoxtestResult$padjFDR = p.adjust(WilcoxtestResult$p, method = "fdr", n = length(WilcoxtestResult$p))
asterisk = paste(padjmethod, "Asterisk", sep = "")
SigTableFinal = WilcoxtestResult
#write.table(SigTableFinal, file="StatisticsResultForFig3F.csv",append = F, quote = F, sep = ",", row.names = F, col.names = T)
padjmethod = "padjFDR"
for (m in 1:length(SigTableFinal[,1])){
  ifelse (SigTableFinal[[padjmethod]][m] < 0.001,
          SigTableFinal[[asterisk]][m] <- "***",
          ifelse (SigTableFinal[[padjmethod]][m] < 0.01,
                  SigTableFinal[[asterisk]][m] <- "**",
                  ifelse (SigTableFinal[[padjmethod]][m] < 0.05,
                          SigTableFinal[[asterisk]][m] <- "*", SigTableFinal[[asterisk]][m] <- "")))
}



# Plot
ForPlot = ForPlot[, c("GroupID", phenotype)]
#calculate plot data
ForPlot <- summarySE(ForPlot, measurevar = phenotype, groupvars ="GroupID")
ForPlot$max=(ForPlot[[phenotype]]+ForPlot$se)+0.3
colnames(SigTableFinal)[1] = "GroupID"
ForPlot = merge(ForPlot, SigTableFinal[c("GroupID", "padjFDRAsterisk")], by = "GroupID", all = T)

#save plot Nip
p1 = ggplot(data = ForPlot[c(1,2),], mapping = aes(x = GroupID, y = .data[[phenotype]], color = GroupID)) + 
  geom_errorbar(aes(ymin = .data[[phenotype]] - se, ymax = .data[[phenotype]] + se), width = .1, color = "black") +
  geom_point(shape = 16, size = 1.5) +
  geom_text(mapping = aes(x = GroupID, y = .data[[phenotype]] + se, label= padjFDRAsterisk)) +
  scale_y_continuous(limits = c(3, 6)) +
  scale_shape_discrete(solid = F) +
  scale_color_manual(values = c("#888888", "#00c8ce")) +
  #00c8ce #fb8d81
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
  )
p1=p1+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
ggsave(p1, filename = "Fig3F_1.pdf", width = 1, height = 2)
#ggsave(p1, filename = "Fig3F_1.png", width = 1, height = 2)

#save plot d14
p2 = ggplot(data = ForPlot[c(3,4),], mapping = aes(x = GroupID, y = .data[[phenotype]], color = GroupID)) + 
  geom_errorbar(aes(ymin = .data[[phenotype]] - se, ymax = .data[[phenotype]] + se), width = .1, color = "black") +
  geom_point(shape = 16, size = 1.5) +
  geom_text(mapping = aes(x = GroupID, y = .data[[phenotype]] + se, label= padjFDRAsterisk)) +
  scale_y_continuous(limits = c(8, 11)) +
  scale_shape_discrete(solid = F) +
  scale_color_manual(values = c("#888888", "#00c8ce")) +
  #00c8ce #fb8d81
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
  )
p2=p2+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
ggsave(p2, filename = "Fig3F_2.pdf", width = 1, height = 2)
#ggsave(p2, filename = "Fig3F_2.png", width = 1, height = 2)
    
#save plot d27
p3 = ggplot(data = ForPlot[c(5,6),], mapping = aes(x = GroupID, y = .data[[phenotype]], color = GroupID)) + 
  geom_errorbar(aes(ymin = .data[[phenotype]] - se, ymax = .data[[phenotype]] + se), width = .1, color = "black") +
  geom_point(shape = 16, size = 1.5) +
  geom_text(mapping = aes(x = GroupID, y = .data[[phenotype]] + se, label= padjFDRAsterisk)) +
  scale_y_continuous(limits = c(5, 8)) +
  scale_shape_discrete(solid = F) +
  scale_color_manual(values = c("#888888", "#00c8ce")) +
  #00c8ce #fb8d81
  xlab("") +
  theme(
    plot.background = element_rect(fill = "#FFFFFF"), 
    panel.background = element_blank(), 
    panel.grid.major.x = element_blank(),
    panel.grid.major.y = element_blank(), 
    panel.grid.minor.x = element_blank(), 
    panel.grid.minor.y = element_blank(),
    panel.border = element_blank(), 
    axis.title = element_text(size = 8),  
    axis.text = element_text(size = 8, vjust = 1, hjust = 1, colour = "#000000"), 
    axis.line = element_line(colour = "#000000"),
    legend.title = element_blank(),
    legend.key = element_rect(fill = "#FFFFFF"),
    legend.position = "none"
  )
p3=p3+theme(axis.text.x=element_text(angle=45,vjust=1, hjust=1))
ggsave(p3, filename = "Fig3F_3.pdf", width = 1, height = 2)
#ggsave(p3, filename = "Fig3F_3.png", width = 1, height = 2)
```

